Leadership across cultures and contexts: an exploratory analysis

### 2020-05-17 leadership_across_cultures_contexts.Rmd

The leader functions cluster analysis (Figure \@ref(fig:cluster)B) also identified two top-level clusters; the larger of which we identified as a management functions cluster (e.g., *Organize cooperation*, *Military command*, *Resolve conflict*) and the smaller of which we identified as a prosociality cluster (e.g., *Social functions*, *Distribute resources*, *Hospitality*). Within the management cluster, we identified two moderately supported subclusters; a *Mediation* subcluster (e.g., *Resolve conflict*, *Provide counsel*), and an *Organization* subcluster (e.g., *Organize cooperation*, *Military command*).

@@

<!-- To explore potential population variation in the *Prestige vs. Dominance* and *In-group favoritism vs. Social Status* leader qualities components and the *Social functions* and *Mediation vs. Organization* leader functions components, we fit four hierarchical linear models at the text-record level, using nested random effects of document within culture with each of these components as outcome measures. For predictor variables we relied on our researcher-coded measure of group structure and our modified version of the HRAF subsistence classification (see Figure \@ref(fig:grouptype)).  -->

>>>>

The leader functions cluster analysis (Figure \@ref(fig:cluster)B) also identified two top-level clusters; the larger of which we identified as a management functions cluster (e.g., *Organize cooperation*, *Military command*, *Resolve conflict*) and the smaller of which we identified as a prosociality cluster (e.g., *Social functions*, *Distribute resources*, *Hospitality*). Within the management cluster, we identified two moderately supported subclusters; a *Strategize* subcluster (e.g., *Resolve conflict*, *Provide counsel*), and an *Organize* subcluster (e.g., *Organize cooperation*, *Military command*).

@@

<!-- To explore potential population variation in the *Prestige vs. Dominance* and *In-group favoritism vs. Social Status* leader qualities components and the *Social functions* and *Strategize vs. Organize* leader functions components, we fit four hierarchical linear models at the text-record level, using nested random effects of document within culture with each of these components as outcome measures. For predictor variables we relied on our researcher-coded measure of group structure and our modified version of the HRAF subsistence classification (see Figure \@ref(fig:grouptype)).  -->
